Estimating individual subjective values of emotion regulation strategies

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted document

@@

@@

@@

The second model explained 0.41 percent of variance.
All results of the second model are in table~@ref(tab:TabMLM\_H5).

@@

\caption{\label{tab:TabMLM_H5}Results of multilevel model predicting subjective values of ER strategies.}

@@

\small{

>>>>

{[}INSERT FIGURE 1 HERE{]}

@@

{[}INSERT FIGURE 2 HERE{]}

@@

Individual SVs could be determined for 120 participants for all three ER strategies.
SVs ranged between 0.005 and 1.00.
In sum, \(n=\) 119 had a SVs of 1.0, indicating a clear preference for one ER strategy.
Highest SV for distraction was reported by \(n=\) 41, for distancing by \(n=\) 36, and for suppression by \(n=\) 36.

@@

The second model explained 0.41 percent of variance.
All results of the second model are in table~\ref{tab:TabMLMH5}.

{[}INSERT TABLE 1 HERE{]}

@@

\caption{\label{tab:TabMLMH5}Results of multilevel model predicting subjective values of ER strategies.}

@@
